\LARGE BAND\\ \Large Decentralized Data Curation Protocol

### 2018-07-17 paper.tex
Bump version: 1.0.0
Fix text size and change subtitle to 'Public Draft'
Bump version: 1.1.0
Fixed typo
Update whitepaper to V2

\documentclass[letterpaper,11pt]{article}
\usepackage{array}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{pdfpages}
\usepackage{changepage}
\usepackage{color}
\usepackage[hyphens,spaces,obeyspaces]{url}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
\usepackage[title]{appendix}
\usepackage{float}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{cleveref}
\usepackage{tikz}
\usepackage{arydshln}
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{positioning}
\usepackage[margin=1.5in]{geometry}
\linespread{1.1}
\setlength{\parindent}{30pt}
\setlength{\emergencystretch}{3em}
\setlength\dashlinedash{0.2pt}
\setlength\dashlinegap{1.5pt}
\tikzstyle{arrow} = [thick,->,>=stealth]
\tikzstyle{utxo} = [
    rectangle, minimum width=3.8cm, minimum height=4cm, text centered, text width=3.8cm,
    scale=0.85, draw=black, font=\ttfamily]
\tikzstyle{contract} = [
    rectangle, minimum width=3.8cm, minimum height=4cm, text centered, text width=3.8cm,
    scale=0.85, draw=black, font=\ttfamily, fill=gray!5]

\title{\LARGE BAND\\
    \Large Unleashing Tokenized Economy}
\author{
        Soravis Srinawakoon\\
        \small\href{mailto:soravis@bandprotocol.com}
            {\nolinkurl{soravis@bandprotocol.com}}
    \and
        Sorawit Suriyakarn\\
        \small\href{mailto:swit@bandprotocol.com}
            {\nolinkurl{swit@bandprotocol.com}}
    }
\date{\today\\\small Draft Version 0.1.4}
\begin{document}

@@

Band Protocol is a decentralized, permissionless blockchain protocol to create tokenized marketplace and token-curated community. Band Protocol enables seamless issuance of personalized Community Token through a continuous bonding curve, a smart contract that mints and burned personalized token through a predefined mathematical function based on current circulating supply. Any entities ranging from businesses, brands and celebrities can create a loyal token-curated community with personalized tokens. Personalized Community Token is a utility token representing primary currency, subscription, discount, reward point, or any other use cases within the community as defined by the Community Manager.

Band Protocol standardizes Product Token as a way for community manager to issue products and services. It enables both tokenized real-world products as well as new digital asset creation such as rare digital collectibles and attention token.

Band Protocol enables the creation of subscription business model. Followers can stake their Community Token to a staking contract and receive regular benefits similar to normal subscription or membership. Band Protocol allows Community Manager to define their subscription tier and discount token. Discount token is a tokenized discount voucher used to reward loyal followers and incentivize active participants rather than speculators. The amount of discounts can be customized by Community Manager and in general is proportionate to the amount of total network value. Discount tokens will be an incentive for loyal followers to stake their tokens and promote the growth of the community.

Band Token is the native utility token on the delegated-proof-of-stake Band Chain. Band Token are used to secure the network, provide global liquidity to every Community Token, and act as a governance token for future protocol upgrade.

@@

\subsection{Tokenized Economy}

A typical market-based economy involves the exchange of goods and services through barter or a medium of exchange. Traditionally, buyers exchange physical coins and banknote with physical products or services offered by sellers. As technology progresses, Internet has enabled digital economy whereby goods and services are being exchanged with digital money. E-commerce experiences exponential growth as people can conveniently conduct transaction with people across the world. Centralized companies start to dominate marketplace platform and payment gateway which are key enablers of the digital economy.

Blockchain and crypto assets are giving rise to yet another revolution in the economy. Bitcoin~\cite{nakamoto}, the first cryptocurrency, becomes the first decentralized currency which enables trustless, censorship-resistant payment. Cryptocurrency such as Bitcoin allows anyone to send transaction to anyone around the world at a fraction of a cost and a fraction of time required for traditional financial institutions to conduct similar transaction. As payment and currency are being tokenized, traditional asset is slower to experience similar tokenization process. Regulation and usability are two key factors that hinder the explosive growth of asset tokenization. Asset tokenization has clear benefits:
\begin{itemize}
\item Global accessibility
\item Liquidity premium
\item Low transaction fee
\item Transparency
\item Security
\end{itemize}

Similar to how physical trade transitions to digital trade by the advancement of the Internet, the next era of commerce is the transition from centralized digital trade to decentralized token trade. Tokenized economy will become prevalent as both real-world assets and payment are being tokenized. Band Protocol enables asset tokenization and creates a standard platform for tokenized economy.
\newpage

\subsection{Token-curated Community}
Typically, economy centers around community with common shared interest. There are multiple layers of community depending on the focus. A country is one big community where everyone shares geographical border, culture, tradition, customs and beliefs. Soccer players and followers together is another community where everyone shares interest in the sport which leads to an economic activity around soccer team and players. This leads to two sides of participant in the community: buyers and sellers. While they share similar interest in the same community, they often have conflicting needs as both sides try to maximize their own utility at the expense of the other side. Soccer team would raise their ticket price as they gain more popularity while their loyal followers have to keep paying more. Conversely, followers will not go out of their way to promote their favorite artist because they have very little economic incentive to do so. Their incentives are not truly aligned.

Crypto asset becomes the answer to which community members can finally have an aligned incentive to grow the community together. A token-curated community is a community centered around a personalized Community Token whose value closely tie to the overall network value of the community. Community Token acts as a shared economic incentive for both buyers and sellers to promote the growth of the community. Band Protocol standardizes the creation of token-curated community and details how personalized Community Token's value can be derived from overall community value through staking and discount mechanism.

%Currently companies, brands and celebrities struggle to engage with their loyal customers and followers. They mostly utilize social media channels such as Facebook, Twitter, and Instagram to cultivate their community. However, it is becoming more difficult to monetize their fan base. Many celebrities try to monetize their followers by advertising products from other companies to their followers, which is not always in the best interest of the community. For example, recent Thai celebrities are facing lawsuit because they advertise non-FDA-approved cosmetics. Influencers accept payment to promote products inorganically which misleads their followers. Similarly, content distributor channel like Youtube and Spotify are taking a big cut from content provider. Newcomers find themselves much more difficult to compete for attention and create network effect, which was originally promised by these platforms.

\subsection{Use Cases}
\begin{itemize}
\item A new musician creates a new community and publishes her first album. She cultivates and rewards early adopters through her Community Token. By having skin-in-the-game token, early adopters rally behind her success and help her grow the community.
\item Bruno Mars issue Bruno Token which can be staked to receive constant discount for all future products, priority queue to purchase concert ticket, and right to access VIP zone during meet and greet session. Bruno Mars also sell rare digital cards which contain non-public photos of the band and digital artwork.
\item Established company creates a community to curate information around a company and reward active participants with community token. Similar to how Barilla encourages followers to post new recipe on Facebook Page, now active participants can receive Barilla Token to purchase Barilla products as an incentive to curate information inside Barilla community.
\end{itemize}

\subsection{BAND Architecture} \label{sec:band-architecture}

BAND architecture consists of three main layers shown in figure~\ref{fig:pyramid}:

\begin{itemize}
\item \textbf{BAND Blockchain Layer} provides backbone blockchain network to support the entire BAND ecosystem. This includes design of cryptographic algorithm for public-private key management, gas allocation, blockchain internal state representation, on-chain price oracle and native BAND Token.
\item \textbf{BAND Protocol Layer} provides standard contracts to facilitate tokenized economy by enabling creation of personalized-token-curated community, tokenized products, token subscription model, discount token, attention curation market, etc.
\item \textbf{Application Layer} is the consumer-facing application that utilize the underlying BAND blockchain and protocol and serve real-world needs. Any developers can create a solution on top of open, permissionless BAND Protocol. Campbase will be the first application built on top of BAND.
\end{itemize}

\begin{figure}[h]
    \centering
    \includegraphics[width=1.05\textwidth]{figures/pyramid}
    \caption{Overview of BAND architecture}
    \label{fig:pyramid}
\end{figure}

\clearpage
\newpage

\section{Blockchain Layer} \label{sec:blockchain-layer}
This section discusses the overview of the blockchain layer in the BAND architecture. Please refer to yellow paper for full formal specification of blockchain states and transactions.

\subsection{Delegated Proof-of-Stake Protocol} \label{sec:dPOS}
BAND Protocol Layer is fundamentally independent of consensus mechanism. Tendermint, which utilizes delegated proof-of-stake, is chosen as the consensus protocol as BAND prioritizes scalability and usability over sovereign-grade security.

\subsubsection{Tendermint}
Tendermint~\cite{kwon2014tendermint} is a partially synchronous Byzantine fault tolerance consensus protocol. In BAND protocol, Tendermint is responsible for connecting the nodes and ensuring that the validators agree on a block, while BAND protocol implements Tendermint's Application BlockChain Interface (ABCI) and is responsible for maintaining the blockchain state and verifying transactions. We decide to use Tendermint in the first stage of development for several reasons:

\begin{itemize}
\setlength\itemsep{0em}
\item Tendermint is widely adopted and well recognized. It is currently used by multiple real-world blockchain systems, such as Cosmos~\cite{cosmoswhitepaper} and OmiseGo~\cite{omgtendermint}. The source code is fully open-source and has undergone public reviews.
\item Tendermint is able to handle more than 10,000 transactions per second with minimal block confirmation time~\cite{tendermint10k}.
\item Tendermint consensus protocol can quickly identify malicious actors, allowing blockchain application to quickly punish them. It is also resistant against most existing attack vectors.
\end{itemize}

\paragraph{Consensus}
In Tendermint, each node that participate in the consensus has a non-negative voting power. To produce a block, more than $\frac{2}{3}$ of the voting power must agree on the block validity. Tendermint allows ABCI to specify the voting power of each node. BAND protocol gives each node a voting power proportionally to the amount of BAND token staked by that node.

\paragraph{Validators}
Tendermint performance will degrade with more number of validators, as more validators introduce more overhead in terms of network communication and node computation. Thus, BAND protocol only allows up to certain number of active validators at any point in time, which is the top $n$ stakers by the amount of staked BAND token. All other stakers will not be able to produce blocks. To circumvent this problem, BAND protocol allows anyone to delegate their staked BAND for another party. With this, stakers can earn from BAND inflation regardless of the amount of BAND they have. Note that if the person one is staking for is acting maliciously, one loses all BAND that was delegated to the malicious person.

\subsubsection{Blockchain Parameters}
\paragraph{Block Size} There is no traditional block size limit. However, a block is limited to contain at most 10,000 transactions. Assuming average transaction size is approximately 100 Bytes, the average maximum block size is 1 Megabytes.

\paragraph{Block Time} The expected block time is 1 second. From experiment, Tendermint is able to consistently handle the workload of 10,000 transactions per second~\cite{tendermint10k}.

@@

\paragraph{Block Reward} We set the inflation rate of 5\% per year as the reward for block validators. Because there are expectedly 31,536,000 blocks per year (1 block per second), the reward per block is $\frac{1}{6307200}$ times the current total BAND token supply.

\paragraph{Block Penalty} Tendermint protocol halts if at least $\frac{1}{3}$ of the voting power fail to accept a proposed block. To disincentivize validators from not participating, validators that have not participated in 300 blocks (5 minutes) lose 1\% of their staked BAND and automatically have all of their BAND unstaked. If a validator acts maliciously, his proposed block will be rejected by majority of the voting power. In that case, the validator lose all of his staked BAND token.

\subsection{Incentives and Fees} \label{sec:incentives-and-fees}
One of BAND protocol's main design goals is ease of usage. We carefully design the protocol to have no explicit transaction fee without introducing vulnerability to the blockchain. To achieve this goal, the transaction doesn't need to include a fee, but instead need to include a gas. The rules work as follows:

\begin{itemize}
\setlength\itemsep{0em}
\item 36,000,000 gas is created every hour, distributed to everyone proportionally to the amount BAND he is currently staking.
\item Every transaction must include exactly one gas. This means there is a hard cap of 36,000,000 transactions per hour, or 10,000 transactions per second.
\item Existing gas is invalidated every hour. At that time, everyone will be able to request a new allocation of gas for the new hour.
\end{itemize}

With this system in place, there is no need for transaction fee. It is possible, however, for a gas to be sold in secondary market for those who need more bandwidth. In the application layer, we expect application owners or community managers to provide gas for users. BAND Protocol allows a transaction to be augmented with gas by a third party without tempering with the transaction information itself.

\subsection{Cryptographic Keys}
This subsection provides a short summary of cryptographic algorithms used in BAND protocol.

\paragraph{Public-Private key pair} BAND protocol uses Ed25519~\cite{bernstein2012high} algorithm for public/private key verification.

\paragraph{Multiple Private keys} BAND protocol promotes the practice of not reusing private key to ensure pseudo-anonymity~\cite{moser2013anonymity}. BAND allows anyone to generate their single \emph{super private key} that acts as a seed to generate more private key with a nonce. A private key is simply $sha256(super\_private\_key + nonce)$. Every address on chain will have an associated nonce, so that the owner can easily generated his private key based on that nonce. Note that the nonce information is not useful to anyone that does not have the super private key.

\paragraph{Address} Similar to Bitcoin~\cite{nakamoto} and Ethereum~\cite{wood2014ethereum}, BAND protocol does not directly use public key as an address. Instead, the last 160 bits (20 bytes) of public key is used as the address. This decision is done to mitigate effect of the unlikely event that Ed25519 is compromised. It also makes the public key not revealable until there is a transaction interacting with it.

\subsection{BAND Protocol State}
BAND's blockchain state is made up of two different object types: unspent transaction output (UTXOs) and static contracts. The subsection provides a high-level overview of the two object types.

\subsubsection{Unspent Transaction Outputs (UTXOs)}
A UTXO represents an amount of tokens owned by a person in the network. BAND UTXOs are conceptually similar to Bitcoin UTXOs, with one subtle difference: there is more than one type of tokens in the network. Once a UTXO is created, its information cannot be changed, though it can be destroyed when being spent. In order to spend a UTXO as part of a transaction, the owner must prove UTXO ownership by signing the transaction with one of his private keys matching the UTXO's owner address. In this paper, a UTXO is depicted as a white rectangular box containing its information.

\subsubsection{Static Contracts}
A static contract is everything else in the blockchain that is not exclusively owned by one party (i.e. not a UTXO). A static contract always has a static address to which UTXOs or transactions in the network can refer to. Once a static contract is created, it stays forever and cannot be destroyed, though the values inside the contract may change as a result of a transaction being processed. In this paper, a static contract is depicted as a grayed rectangular containing its information.

\begin{figure}[!h]
\centering
\begin{tikzpicture}[node distance=7cm]
\node (node1) [utxo] {
    owner = Alice \\
    token = BAND \\
    amount = 10
};

\node (node2) [contract,right of=node1] {
    addr = 0x1234 \\
    name = The Rock \\
    manager = Rock \\
    supply = 100 \\
    eq = $s^2 + 10s$
};
\end{tikzpicture}
\caption{Left box is a UTXO representing 10 BAND token owned by Alice. Right box is a contract representing the current state of community token ``The Rock'' living at static address {\tt 0x1234}, with Rock as the community manager, current token supply of 100 The Rock, and value-supply equation of $V(s) = s^2 + 10s$.}
\label{fig:utxo-contract-example}
\end{figure}

\subsection{On-Chain Price Oracle} \label{sec:on-chain-px-oracle}
BAND protocol is built to be aware of external off-chain price information. This allows on-chain fiat pricing in Product Token insurance contracts (\Cref{sec:product-token}), tradable UTXOs (\Cref{sec:marketplace}), and permission contracts (\Cref{sec:permission-contracts}). To achieve this goal, BAND protocol requires that every block must contain the following price information. Note that this list can be extended later as necessary.

\begin{itemize}
\setlength\itemsep{0em}
\item $P_{\mathit{BNDUSD}}$ : The volume-weighted average price of BAND token and US Dollar across all cryptocurrency exchanges.
\item $P_{\mathit{EURUSD}}$ : The conversion rate between Euro and US Dollar.
\item $P_{\mathit{GBPUSD}}$ : The conversion rate between British Pound and US Dollar.
\end{itemize}

For a block with price information to be committed, the majority of consensus participants must agree on the price values (Refer to~\cref{sec:dPOS} for consensus detail). Nodes will accept any price within 1\% error threshold. To prevent one bad price from having a direct influence on the token pricing, the protocol uses the median price among 120 consecutive blocks as one valid price data point. Given block time of one second, a single data point comes from a median price over a period of two minutes. Additionally, to prevent short-term price manipulation, on-chain price is the median among last 30 data points. Thus a price at any point is the median of price in the past one hour. Notice that with this approach, the on-chain price will not change more frequently than every two minutes. This reduces chances of transaction, which derives BAND token price based on $P_{\mathit{BNDUSD}}$, getting invalidated when the blockchain is backlogged and potentially lead to more backlogged transactions.

\begin{figure}[!ht]
 \begin{adjustwidth}{-0.5cm}{}
\begin{tabular}{c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c}
 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10& 11& 12& 13& 14& 15\\ \hline
datapoint 1 & {\color{cyan} 32} &7 &66 &{\color{cyan} 42} &55 &67 &61 &41 &38 &1 &{\color{cyan} 27} &59 &33 &45 &21 \\
datapoint 2& 18 &52 &{\color{cyan} 62} &60 &{\color{blue} 37} &64 &75 &65 &{\color{cyan} 35} &34 &5 &3 &15 &14 &56 \\
datapoint 3& 8 &{\color{cyan} 44} &74 &29 &23 &{\color{cyan} 43} &{\color{cyan} 48} &17 &25 &51 &4 &46 &{\color{cyan} 36} &{\color{cyan} 39} &69 \\
datapoint 4& 47 &70 &12 &71 &49 &30 &13 &20 &53 &{\color{cyan} 9} &73 &{\color{cyan} 26} &54 &63 &72 \\
datapoint 5& 40 &31 &58 &19 &16 &10 &28 &{\color{cyan} 24} &22 &2 &57 &11 &50 &6 &{\color{cyan} 68} \\
\end{tabular}
\caption{Illustration of median of medians algorithm over 75 data points split into 15 groups of 5. Cyan numbers are the medians of their groups. The median of medians is shown in blue. In BAND protocol, price information for each group is collected every second over the period of 2 minutes (group size of 120). The on-chain price is the median over the most recent 30 groups.}
\end{adjustwidth}
\end{figure}

\subsection{BAND Token}
BAND token is the primary network token native to BAND Protocol. At blockchain level, an amount of BAND tokens is represented as a UTXO containing the amount and its owner's address. BAND token serves three primary functionalities.
\begin{enumerate}
\setlength\itemsep{0em}
\item Secure the network and prevent network spam through staking.
\item Act as network token to provide global liquidity to each of the Community Tokens through continuous bonding curve model.
\item Serve as a future governance token to vote on protocol upgrade as well as curating a list of future communities.
\end{enumerate}

\subsubsection{Staking}
The protocol allows network participants to stake their BAND tokens in exchange for consensus voting power (See~\cref{sec:dPOS}) and network bandwidth (See~\cref{sec:incentives-and-fees}). To stake BAND token, the owner of a BAND UTXO sends a {\tt STAKE} transaction to the network transforming the BAND UTXO into a staked BAND UTXO of the same amount. To un-stake the token, the owner sends an {\tt UNSTAKE} transaction, effective undoing the previous {\tt STAKE} transaction. Staked BAND UTXOs are different from UTXO because they cannot be spent until they get transformed back to BAND UTXOs.

\begin{figure}[!h]
\centering
\begin{tikzpicture}[node distance=7cm]
\node (node1) [utxo] {
    owner = Alice \\
    token = BAND \\
    amount = 10
};

\node (node2) [utxo, right of=node1] {
    owner = Alice \\
    token = BAND\_STKD \\
    amount = 10
};

>>>>

\documentclass[letterpaper,11pt]{article}
\usepackage{array}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{pdfpages}
\usepackage{changepage}
\usepackage{color}
\usepackage[hyphens,spaces,obeyspaces]{url}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
\usepackage[font=footnotesize,labelfont=bf]{caption}
\usepackage[title]{appendix}
\usepackage{float}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{cleveref}
\usepackage{tikz}
\usepackage{arydshln}
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{positioning}
\usepackage[margin=1.5in]{geometry}
\linespread{1.1}
\setlength{\parindent}{30pt}
\setlength{\emergencystretch}{3em}
\setlength\dashlinedash{0.2pt}
\setlength\dashlinegap{1.5pt}
\tikzstyle{arrow} = [thick,->,>=stealth]
\tikzstyle{utxo} = [
	rectangle, minimum width=3.8cm, minimum height=4cm, text centered, text width=3.8cm, 
    scale=0.85, draw=black, font=\ttfamily]
\tikzstyle{contract} = [
	rectangle, minimum width=3.8cm, minimum height=4cm, text centered, text width=3.8cm, 
    scale=0.85, draw=black, font=\ttfamily, fill=gray!5]

\title{\LARGE BAND\\
	\Large Decentralized Data Curation Protocol}
\author{
		Soravis Srinawakoon\\
		\small\href{mailto:soravis@bandprotocol.com}
			{\nolinkurl{soravis@bandprotocol.com}}
	\and 
		Sorawit Suriyakarn\\
		\small\href{mailto:swit@bandprotocol.com}
			{\nolinkurl{swit@bandprotocol.com}}
	}
\date{July 17, 2018 \\\small Public Draft Version 2.0.0}
\begin{document}

@@

Online data in digital community is often unreliable. Centrally curated data source is biased or provide no access for the general public. Paid reviews are engaged to provide biased reviews of products or places. On the other hand, public data in open community such as various social media platforms are unreliable because there is no incentive for people to moderate such content. One can observe many fake news in recent U.S. Presidential Election, phlishing bots on Twitter, or fake upvotes on Reddit to further one's own agenda. Data is becoming more and more essential in the new information age and undeniably there is a general need for reliable online data source.

Band Protocol is a decentralized data curation protocol. Our protocol incentivizes curators around the world to coordinate and ensure reliable data through token staking and bonding curve mechanism. We propose a solution where database or registries can be created around personalized tokens - which are used as an economic incentive for people to curate and moderate data while punish those that propose inaccurate information. These information can be organized as a token-curated registry or other forms of data, Band Protocol is a general blockchain protocol to create token-curated registries and communities, each with its own token and bonding curve.

Band Token is the native utility token on the delegated-proof-of-stake Band Chain, built on top of Tendermint with Plasma implementation. Band Token is used to secure the network, provide global liquidity to every Community Token, and act as a governance token for future protocol upgrade.

@@

\subsection{Token-curated Registry}

Data is the new oil in the technological era. End-users desire access to trusted, curated source of data. This applies to every industry: list of curated cryptocurrency news, list of trusted advertisers, best restaurants in San Francisco, top business schools, whitelisted wallets for security token traders, blacklisted wallet for known hackers, etc. Such data is traditionally curated by a central source of authority which is often biased and provide no transparency to the general public.

Token-curated registry (TCR) is a structured dataset, often referred to as a list, which is decentrally curated by token holders. TCR uses token to assign voting right proportional to the number of tokens held. Band Protocol is a standard protocol to issue TCR, each with its own intrinsic token. Token's value links directly to the usefulness of that particular TCR. If the TCR is useful and there are followers, there will be market demand for applicants to buy tokens and submit their data to be included within the dataset.

\subsection{Why Blockchain and Tokens}

Decentralized curation lacks quality because previously there is no incentive for moderation. Blockchain enables the creation of new asset class, cryptographic token, which acts as an economic incentive to trustlessly coordinate people around a certain objective. Bitcoin~\cite{nakamoto} is an economic incentive for miners to stay honest with transaction verification and make it extremely expensive to attack the network.

In a similar fashion, token becomes an economic incentive for curators to submit and verify data in Band Protocol. To ensure integrity, token staking mechanism is necessary to incentivize honesty. Tokens make it economically irrational for bad data to exist in the database. If curated dataset is useful, it will attract more followers and users who in turn attract more applicants who wish to submit data to be included within the list. Token holders can make money by challenging bad data submission and by curating useful dataset. If token holders are biased in their curation, data becomes useless. There will be no followers, no applicants and thus it materially affects their token's value. It is in their best interest to curate the most useful set of data.

\subsection{Band Architecture}
Band blockchain, though primarily created as a data curation platform, is engineered as a generic smart contract runtime system, with a collection of handcrafted, specialized contracts for business logic. Band blockchain consists of two primary layers.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.95\textwidth]{bandchain}
	\captionsetup{labelformat=empty}
    \caption{Overview of Band architecture. Right: dPOS consensus based on Tendermint implementation. Left: Monolithic C++ Band application consisting of multiple smart contracts that connect together through Band native token.}
    \label{fig:pyramid}
\end{figure}

\subsubsection{Blockchain Layer}
This layer is responsible for ensuring that all nodes (1) agree on the same on-chain data and transactions, (2) apply the same bandwidth limit logic, and (3) execute the same smart contract code. One can think of this layer as an Ethereum-like blockchain that supports any turing-complete smart contracts, though with a significantly higher number of transactions per second (approximately 3000 TPS) and a feeless incentive model.

\subsubsection{Band Protocol}

Band protocol is a collection of smart contracts designed to support running data curation platforms. Smart contracts are C++ native objects with direct access to other contracts and blockchain information.  The contracts are bundled together in a single blockchain release, and together responsible for providing Band protocol functionalities.

We design the blockchain this way to achieve 4 major design goals: performance, simplicity, extensibility, and scalability.

\paragraph{Performance}
Band blockchain logic, including smart contracts execution, is written completely in the C++ programming language with direct focus on code performance. Because smart contracts are compiled together with the core logic \emph{monolithically} into a single native executable binary, complex whole-program optimization~\cite{chambers1996whole} can be applied. Additionally, because smart contracts are linked statically, there is zero runtime overhead of interpreters or virtual machines, which is different from mainstream smart contract blockchains such as Ethereum, NEO, and EOS~\cite{wood2014ethereum,neowhitepaper,eoswhitepaper}.

\paragraph{Simplicity}
The core blockchain layer logic does not impose any assumption on business logic, making it very lightweight. For instance, the decision to use cryptographic signature for accounts is at the smart contract level, with Ed25519~\cite{bernstein2012high} used by the default Band Account contract, similar to the yet-to-be-implemented EIP-86 proposal~\cite{eip86,eip86research}. This independent structure makes the platform easy to change and easy to verify correctness.

\paragraph{Extensibility}
Being fundamentally an open-source smart contract runtime system, Band blockchain can be extended with more functionalities merely by adding more smart contracts. In the future, if there is a discovery of an innovative data curation method, such algorithm can be written as a Band smart contract, verified its correctness, and incorporated seamlessly into Band blockchain. This extensible nature also allows the community to fork Band blockchain to more functionalities if deemed necessary.

\paragraph{Scalability}
Band blockchain is designed to support Plasma scalability paradigm~\cite{poon2017plasma} from day zero. The plasma contract is part of Band protocol and that potentially extends the blockchain to support millions of transactions per second in parallel without compromising blockchain security.

\section{Blockchain Layer} \label{sec:blockchain-layer}
This section describes the architecture of the blockchain layer of Band chain. For non-technical reader, feel free to skip to Band Protocol in~\cref{sec:band-protocol}

\subsection{Delegated Proof-of-Stake Consensus} \label{sec:dPOS}
Band blockchain uses delegated proof-of-stake consensus mechanism to ensure that the state of the world are consistent among all running nodes. Band chain is implemented as a Tendermint ABCI application.

\subsubsection{Tendermint}
Tendermint is a partially synchronous Byzantine fault tolerance consensus protocol. In Band system, Tendermint is responsible for connecting the nodes and ensuring that all validators agree on a block, while Band blockchain implements Tendermint's Application BlockChain Interface (ABCI) and is responsible for maintaining the blockchain state and verifying transactions. We decide to use Tendermint in the first stage of development for several reasons:

\begin{itemize}
\setlength\itemsep{0em}
\item Tendermint is widely adopted and well recognized. It is currently used by multiple real-world blockchain systems, such as Cosmos~\cite{cosmoswhitepaper} and OmiseGo~\cite{omgtendermint}. It is open-source and has undergone public reviews.
\item Tendermint is theoretically able to handle more than 10,000 transactions per second~\cite{tendermint10k} with minimal block confirmation time. In practice, we are able to consistently maintain 3,000 transactions per second when running Tendermint with Band application.
\item Tendermint consensus protocol can quickly identify malicious actors, allowing blockchain application to quickly punish them. It is also resistant against most existing attack vectors~\cite{buchman2016tendermint} in the consensus level. 
\end{itemize}

\paragraph{Consensus}
In Tendermint, each node that participates in the consensus has a non-negative voting power. To produce a block, more than $\frac{2}{3}$ of the voting power must agree on the block validity. Tendermint allows ABCI to specify the voting power of each node. Band protocol gives each node a voting power proportionally to the amount of Band token staked by that node to the validating contract (See~\cref{subsec:stake} for stake contract).

\paragraph{Validators}
Tendermint performance will degrade with more number of validators, as more validators introduce more overhead in terms of network communication and node computation. Thus, Band protocol only allows up to certain number of active validators at any point in time, which is the top $n$ stakers by the amount of staked Band token. All other stakers will not be able to produce blocks. To circumvent this problem, Band protocol allows anyone to delegate their staked Band for another party. With this, stakers can earn from Band inflation regardless of the amount of Band they have. Note that if the person one is staking for is acting maliciously, one loses all Band that was delegated to the malicious person.

\subsubsection{Blockchain Parameters}
\paragraph{Block Size} There is no traditional block size limit. However, a block is limited to contain at most 3,000 transactions. Assuming an average transaction size is approximately 200 Bytes, the average maximum block size is 600 Kilobytes.

\paragraph{Block Time} The expected block time is 1 second.

@@

\paragraph{Block Reward} We set the inflation rate of 5\% per year as the reward for block validators. Because there are expectedly 31,536,000 blocks per year (1 block per second), the reward per block is $\frac{1}{6307200}$ times the current total Band token supply.

\paragraph{Block Penalty} Tendermint protocol halts if at least $\frac{1}{3}$ of all the voting power fail to accept a proposed block. To disincentivize validators from not participating, validators that have not participated in the past 60 blocks (1 minute) are automatically have all of their Band unstaked. If a validator acts maliciously, such as by proposing more than one block on the height,  it loses all of the staked Band token.

\subsection{Band Token}
Band token is the primary network token native to Band Protocol. Band token serves three primary functionalities.
\begin{enumerate}
\setlength\itemsep{0em}
\item Secure the network and prevent network spam through staking.
\item Act as network token to provide global liquidity to each of the Community Tokens through continuous bonding curve model.
\item Serve as a future governance token to vote on protocol upgrade.
\end{enumerate}

\subsubsection{Staking} \label{subsec:stake}
The protocol allows network participants to stake their Band token in exchange for consensus voting power (See~\cref{sec:dPOS}). The blockchain allows user to stake their Band token via the stake contract created at genesis time (See ~\cref{subsec:blockchain-level-contracts}).

\subsubsection{Bonding}
Band tokens are used as collateral to issue any Community Token through a continuous bonding curve. After bonding curve is set initially in smart contract, anyone can buy Community Token by sending Band token to the contract. Conversely, anyone can sell Community Token back to the contract to receive Band Token. The buying and selling prices are algorithmically adjusted based on the Community Token's circulating supply and the bonding curve equation. Please refer to~\cref{sec:community-token} for more technical discussion regarding Community Token.

Similar to how there is a long tail of {\tt ERC20} tokens, there will be a long tail of less liquid Community Token as data are fragmented. Band token acts as a network token to provide global liquidity between all Community Token and thus anyone can buy, sell or switch between any Community Token with instant liquidity.

\subsubsection{Governance} \label{subsubsec:govern}
Once Band protocol is deployed and used to create multiple token-curated registries, its internal logic cannot be changed easily. To upgrade, one must deploy new contract that may potentially fork the community and cause disruption among existing, working TCR. Upgrade can affect security and usability of the system and therefore cannot be taken lightly. Band Token will act as a governance token for stakeholders in every TCR to vote for future decentralized upgrade and governance issues. This ensures that every stakeholders will thoroughly vet new protocol upgrades and vote in favor of those that truly align with the best interest of the communities.

\subsection{Smart Contract Execution}
In Band blockchain, a smart contract is represented by a C++ class implementation with internal states and methods, some of which are deemed callable. The blockchain state is abstractly a mapping from a 20-byte address to a contract object together with its states. A blockchain transaction encodes a method call at a particular address with a certain list of parameters. Smart contracts have access to the following global variables.

\paragraph{Actor}  The address of the transaction’s actor. Contract can set this variable to its own address. Normally, an account contract will set this variable after verifying the transaction signature, before delegating the transaction processing to another contract. (See Account Contract).
\paragraph{Timestamp} The time at which this block is produced, as specified by the block proposer.
\paragraph{Transaction Hash} The 32-byte {\tt sha256} hash of this transaction.
\paragraph{Block Hash} The 32-byte hash of this block.
\paragraph{Block Height} The integer representing the height of this block.
\paragraph{Block Proposer} The 20-byte address of the block proposer.

\subsection{Blockchain-Level Smart Contracts} \label{subsec:blockchain-level-contracts}
Band blockchain comes with a set of built-in smart contracts to handle primitive operations.

\paragraph{Creator Contract} There is one creator contract created at genesis. This contract provides an interface for a transaction to add another contract to the blockchain. The creator also determines the address of the contract that will be created.

\paragraph{Account Contract} An account contract is responsible for verifying transaction validity, setting the transaction actor, and propagating the transaction to the target contract. The default account contract uses Ed25519 cryptographic algorithm to verify signature. The blockchain, however, can support other means of verification merely by adding more account contracts.

\paragraph{Token Contract} A token contract keeps track of the number of a particular token that each address has. The contract provides similar functionality as the ERC-20 contract. Band protocol, however, extends this contract to support continuous bonding curve between different tokens (see~\ref{sec:community-token}). There is one token contract at genesis for Band token.

\paragraph{Stake Contract} A stake contract allows any address to transfer the contract’s specified token into it. There is one stake contract at genesis used to determine the voting power of the validators. Additionally, stake contracts may be used to create a subscription model, in which a permissioned side-chain (See~\cref{sec:permissioned-community}) allows members to access its information only if they maintain community tokens staked more than a certain threshold.

\subsection{Incentives and Fees}
One of Band protocol's main design goals is ease of usage. We carefully design the protocol to have no explicit transaction fee without introducing vulnerability to the blockchain. To achieve this goal, each transaction doesn't need to include a fee. However, a transaction will be included into a block only when the sender has sufficient bandwidth under the following rules.

\begin{itemize}
\setlength\itemsep{0em}
\item At genesis, the blockchain is assigned two parameters $max\_txs$ to be the maximum transactions per block that the blockchain is able to handle, and $multiplier$ to be 1. 
\item At any block, the block proposer limits the maximum number of transactions for a particular address to the number of Band the address has multiplied by $multiplier$ and $max\_txs$ divided by the total Band supply.
\item If the last block contains less than $max\_txs / 2$ transactions, the multiplier gets doubled. If the last block contains equal to or more than $max\_txs$, the multiplier gets halved.
\end{itemize}

Following the aforementioned rules, each user is entitled to use the network capacity proportional to the amount of Band he or she owns. Note that if the blockchain is underutilized, it will allow more transactions per second to user with lower number of Band. Due to factor of 2 change in $multiplier$ the blockchain can adjust the value in a very reactive manner, e.g. it only takes 30 seconds (30 blocks) to scale the value up by the factor of \emph{1 billion} if the network is not fully utilized, practically allowing any transaction from anyone to get processed.
